<<<<<<< HEAD
---
title: "R Markdown Presentation & Plotly"
author: "Avinash Dodda"
date: "August 02, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Mtcars Scatter plot
<font size="3">The following plot shows the variation of MPG of cars with increasing weight and number of cylinders. The colour code represents the number of cylinders. </font>
```{r cars, message=FALSE, warning=FALSE}
library(plotly)
data("mtcars")
p<- plot_ly(mtcars, x=mtcars$wt ,y=mtcars$mpg, mode="markers",color = as.factor(mtcars$cyl)) %>%
  layout(
    xaxis = list(title = "Weight(1000 lbs)"),
    yaxis = list(title = "MPG")
    )
p
```

## Thank You

=======
---
title: "R Markdown Presentation & Plotly"
author: "Avinash Dodda"
date: "August 02, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Mtcars Scatter plot
<font size="3">The following plot shows the variation of MPG of cars with increasing weight and number of cylinders. The colour code represents the number of cylinders. </font>
```{r cars, message=FALSE, warning=FALSE}
library(plotly)
data("mtcars")
p<- plot_ly(mtcars, x=mtcars$wt ,y=mtcars$mpg, mode="markers",color = as.factor(mtcars$cyl)) %>%
  layout(
    xaxis = list(title = "Weight(1000 lbs)"),
    yaxis = list(title = "MPG")
    )
p
```

## Thank You

>>>>>>> 92c04b5582705ec9041d927519c5558e14ab2c71
