---
title: "R Markdown and Leaflet"
author: "Avinash Dodda"
date: "August 01, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

This project creates a web page using R Markdown that features a map created with Leaflet.

## Goal 

The goal is to mark the **top 10 most populous cities of the United States** on a map.

## Data 

The population data is sourced from following Wikipedia link.

https://en.Wikipedia.org/wiki/List_of_United_States_cities_by_population

## Load and Clean Data

```{r load_data, message=FALSE, warning=FALSE,comment=""}
#load required libraries
library(XML)
library(RCurl)
library(rlist)
library(stringr)
library(tidyr)
library(varhandle)
library(leaflet)

#read data from link
url <- getURL("https://en.Wikipedia.org/wiki/List_of_United_States_cities_by_population")
tables <- readHTMLTable(url, header=TRUE, colClasses = "character")
tables <- list.clean(tables, fun = is.null, recursive = FALSE)
n.rows <- unlist(lapply(tables, function(t) dim(t)[1]))
dt <- as.data.frame(tables[[which.max(n.rows)]])

#clean data and extract top 10 cities
df <- dt[1:10,c(1:4,11)]
colnames(df) <- c("2018 Rank","City","State","2018 Population", "Location")
df$City <- as.character(df$City)
df$City <- str_replace(df$City, "\\[.*\\]", "")
df$State <- as.character(df$State)

df$`2018 Population` <- unfactor(df$`2018 Population`)
df$`2018 Population` <- as.numeric(gsub(",","",df$`2018 Population`))

df<- df %>% 
        separate(Location, c("Lat","Long"),";")
df$Lat <- as.numeric(str_sub(df$Lat,-7,-1))
df$Long <- as.numeric(str_sub(df$Long,1,8))

# check output dataframe used for map
df
```

## Map
The map shows **clusters** of top 10 populous cities in United States. As we zoom in, the markers appear and clicking on markers shows the following information.

- City, State
- Rank
- Population

```{r map}
df  %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(),
          lng=df$Long, 
             lat=df$Lat, 
             popup=paste(df$City,",",df$State,"<br>Rank: ",df$`2018 Rank`,  "<br>Population: ",
                         formatC(df$`2018 Population`, format = "d", big.mark = ",")
                        )
            )

```

